Entropy-SGD: Biasing Gradient Descent Into Wide Valleys

### 2017-01-12 doc/rebuttal.txt

Comment 3) above is for HVP of the loss function of a general deep network, not local entropy. Indeed, HVPs can be computed using forward differencing with two back-props. Such an approximation is susceptible to numerical errors --- especially in high dimensions [P94, M10]. One typically averages the HVP over many samples in the dataset which is expensive, for instance, the authors in [LSP93] average over a few hundred samples, which roughly translates to 5-10x the time required for one iteration of vanilla SGD. More accurate algorithms like that of [P94] also require this averaging over samples.

One could argue that accuracy in the approximation of HVP does not matter in practice for purposes of training; what matters is only the local curvature at a scale commensurate with the typical weight updates. The perturbation vector for computing HVPs using back-props thus needs to be chosen carefully. If so, indeed, approximate computation of HVP can be considered cheap.

[LSP93] LeCun, Yann, Patrice Y. Simard, and Barak Pearlmutter. "Automatic learning rate maximization by on-line estimation of the Hessian’s eigenvectors." NIPS (1993).
[P94] Pearlmutter, Barak A. "Fast exact multiplication by the Hessian." Neural computation 6.1 (1994): 147-160.
[M10] Martens, James. "Deep learning via Hessian-free optimization." ICML (2010).

-----------------------------------------------------------------------

REBUTTAL

We thank the reviewers and the area chair for their insightful feedback. We have incorporated all comments into our current draft. We first discuss the updates to the paper that address common questions raised by the reviewers. We have posted comments to each reviewer to address specific questions.

Updates
-------

a) We have updated the experimental section of the paper with new experiments on MNIST, CIFAR-10 and two datasets on RNNs (PTB and char-LSTM). We also modified the algorithm to increase the value of the scoping parameter \gamma as training progresses instead of fixing it (Sec. 4.3). As a result of this, we can now train all our networks with only the local entropy loss instead of treating it as a regularizer (Eqn. 6).

We obtain significant speed-ups with respect to earlier results due to scoping of the parameter \gamma and the wall-clock training time for all our networks with Entropy-SGD is now comparable to SGD/Adam. In fact, Entropy-SGD is twice as fast as SGD on our experiments on RNNs and also obtains a better generalization error (cf. Fig. 6). The acceleration for CNNs on MNIST and CIFAR-10 is about 20%.

b) Improved exposition of the algorithm in Sec. 4.2 and discussion of experiments in Sec. 5.3, 5.4 that includes intuition for hyper-parameter tuning.

c) Appendix C discusses the possible connections to variational inference (this is the same as the discussion with the AC below). Sec. C.1 presents a comparison of local entropy and SGLD. We note here that our results using Entropy-SGD for both CNNs and RNNs are much better than SGLD is significantly smaller (~3x) wall-clock times.

d)

Response to the reviewers:
-------------------------

a) comment about speed
We now plot the error curves in Figs. 4, 5 and 6 against the "effective number of epochs", i.e., the number of epochs of Entropy-SGD is multipled by the number of Langevin iterations L (we set L=1 for SGD/Adam). Thus the x-axis is now a direct measure of the wall-clock time (agnostic to the underlying implementation and proportional to the number of back-props as suggested), which makes the comparison fair.

b) smoothing of the original loss vs. local entropy
We discuss this in detail in the related work in Sec. 2 and Appendix C. While smoothing the original loss function using convolutions or averaging gradient over perturbations of weights reduces the ruggedness of the energy landscape, it does not help with sharp, narrow valleys. Local entropy introduces a measure that focuses on wide local minima in the energy landscape which is the primary reason for its efficacy. Smoothing the loss function can also, for instance, generate an artificial local minimum between two sharp valleys separated by a tall energ barrier which is detrimental to generalization.

c) unrealistic eigenvalue assumption in Sec. 4.3
We have clarified this point in Remark 4. Our analysis employs an assumption that the Hessian \nabla^2 f(x) does not have eigenvalues in the set [-2\gamma-c, c]. This is admittedly unrealistic, for instance, the eigenspectrum of the Hessian at a local minimum in Fig. 1 has a large fraction of its eigenvalues almost zero. Let us however remark that the bound on uniform stability in Thm. 3 by Hardt et al. assumes global conditions on the smoothness of the loss function; one imagines that Eqn. 9 remains qualitatively the same (with respect to the number of training iterations in particular) even if this assumption is violated to an extent before convergence happens. Obtaining a rigorous generalization bound without this assumption would require a dynamical analysis of SGD and seems out of reach of the current literature.

------------------
AnonReviewer4:

>> how to reconcile "Entropy-SGD obtains better generalization but results in lower cross-entropy loss"
The confusion is probably caused by our omission, it should read "lower cross-entropy loss on the training set" and is fixed now. This experimental insight suggests that there exist wide valleys that are deeper in the energy landscape that generalize well; (possibly) Entropy-SGD manages to find them while SGD gets stuck at a higher loss.

>> the parameter \rho is used on CIFAR-10
We have modified the algorithm to only train with local entropy (i.e., \rho = 0 always). Using scoping we can obtain better results both in terms of generalization error and wall-clock time.

>> also discuss similarities to Hochreiter and Schmidhuber '97 [HS97]
We have modified our discussion of HS97 in Sec. 2. While the motivation is exactly the same, the similarities with their formulation are few and only superficial, e.g., in a flat minimum, the local entropy is a direct measure of the width of the valley, this is conceptually similar to their usage of Hessian. We agree with the reviewer that the elaborate analysis of generalization of HS97 using the Gibbs formalism is a promising direction. In our case, we benefit from similar technical results introduced for uniform stability [BE02].

>> experiments are on a toy example
Please note that our results on CIFAR-10 are close to the best result on non-augmented CIFAR-10 (6.55% error using ELU units) and certainly the best reported result for All-CNN-BN which is a medium-sized model with about 1.6 million weights. The largest model we experimented with is an LSTM on the PTB dataset with 66 million weights, please see the updates above for more details.

[BE02] Olivier Bousquet and Andre Elisseeff. Stability and generalization. JMLR, 2002.

------------------
Csaba Szepesvari:

>> discussion of Baldassi et. al. '16 in related work
We have expanded the discussion of local entropy previously introduced by Baldassi et. al. in Sec. 2. This paper builds upon their work and generalizes it to models with continuous variables, deep networks in particular. After posting the first version of this paper, we have collaborated with Baldassi et. al. on experiments with scoping techniques and they have co-authored this version of the paper.

Please see the "updates to the paper" comment above for the response to the questions regarding (i) eigenvalue assumption, (ii) more thorough experimental results and, (iii) smoothing the loss vs. local entropy.

------------------
AnonReviewer1:

>> Eqn. 8 should have f(x')
Thanks, it is fixed now.

>> experiments on RNNs
Please see updates to the paper above (a), we have included results for word-level and character-level text prediction on PTB and char-LSTM with War and Peace. We not only obtain a better test perplexity than a competitive baseline with SGD, but also train in half as much wall-clock time.

------------------
AnonReviewer2:

4. We set c from Thm. 3.12 of Hardt's paper to be 1 for clarity (c is the initial learning rate). Including it in the exponent does not change our analysis.

------------------
Areachair1 [Stefano should maybe edit and post that comment]:

Re: You should make these connections clearer and more explicit
We have discussed this in depth with sufficient technical details above. Using terms like "similar to motivations of Bayesian methods" and "using Bayesian methods in the inner loop" is generalizing to the point of absurdity.

It is not accurate to term local entropy as "SVI with a moving prior" for a number of reasons. "SVI with a moving prior" has no theoretical basis. It is not connected to the log-likelihood of data, it is connected to local entropy instead. As we have discussed above, local entropy *resembles* SVI with a moving prior but only in an extremely non-rigorous and merely conceptual fashion.

We have updated the experiments in our paper. We now plot the number of gradient evaluations on the x-axis and using scoping, we can in fact show that local entropy performs better in a smaller amount of time. As requested, we have also added a section comparing local-entropy with SGLD.

Re: Exact Hessian-vector product is easy to compute
We have discussed this above (see the comment regarding [P94]). Computing the "exact" HVP requires averaging over the entire dataset, i.e., ~4x the complexity of one epoch, which is expensive.

### 2017-01-12 doc/chaudhari.choromanska.ea.iclr17.tex
wip on rebuttal

\pc{Recent works on shallow networks with discrete weights~\citep{baldassi2015subdominant,baldassi2016unreasonable} have shown that the geometrical structure of the energy landscape is characterized by the existence of an exponentially large number of local minima, a large number of narrow isolated minima, and few very dense regions of minima. These dense states have been discovered analytically by adopting an appropriate local entropy measure, and have been shown to be both algorithmically accessible and to have good generalization properties in both random and real-world settings. The original analysis was done in the case of binary weights, and was later generalized by~\citet{baldassi2016multilevel} to the case of weights with an arbitrary number of precision bits. Here, we generalize this approach to the case of deep architectures and continuous weights, and develop a Langevin stochastic gradient descent algorithm based on the local entropy measure.}{I moved this paragraph to the related work section (grey paragraph). The material and citations are preserved. Please feel free to change it.}

This paper presents a new optimization tool for deep learning designed to exploit the local geometric properties of the objective function. \pc{The existence of wide minima in deep networks is also suggested by the spectral analysis of the Hessian~\citep{sagun2016singularity}.}{we can certainly add this sentence back, but I removed it for the following reasons, (i) their experiments are quite imprecise, (ii) the eigenspectrum is qualitatively different from ours, I suspect they are using forward-differencing to compute it / not averaging over the dataset etc., and (iii) we have done these experiments completely independently and it does not make sense to cite them before even presenting our own results} Consider the histogram in Fig.~\ref{fig:lenet_hessian} showing the spectrum of the Hessian at an extremum discovered by Adam~\citep{kingma2014adam} for a convolutional neural network on MNIST~\citep{lecun1998gradient} with about $47,000$ weights (cf.\@ Sec.~\ref{ss:expt:universality}). It is evident that:
\begin{enumerate}[(i)]
\item a large number of directions ($\approx 94\%$) have near-zero eigenvalues (magnitude less than $10^{-4}$),
\item positive eigenvalues (right inset) have a long tail with the largest one being almost $40$,
\item negative eigenvalues (left inset), which are directions of descent that the optimizer missed, have a much faster decay (the largest negative eigenvalue is only $-0.4$).
\end{enumerate}
Interestingly, this trend is not unique to this particular network. Rather, its qualitative properties are shared across a variety of network architectures, sizes, datasets or optimization algorithms (refer to Sec.~\ref{s:expt} for more experiments). Local minima that generalize well and are discovered by gradient descent lie in ``wide valleys'' of the energy landscape, rather than in sharp isolated minima. For an intuitive understanding of this phenomenon, imagine a Bayesian prior concentrated at the minimizer of the expected loss, the marginal likelihood of wide valleys under this prior is much higher than narrow, sharp valleys even if the latter are close to the global minimum in training loss. Almost-flat regions of the energy landscape are robust to data perturbations, noise in the activations, as well as perturbations of the parameters, all of which are widely-used techniques to achieve good generalization. This suggests that wide valleys should result in better generalization and, indeed, standard optimization algorithms in deep learning seem to discover exactly that --- without being explicitly tailored to do so. \pc{For a more detailed recent
analysis of the Hessian, see the parallel work of~\citet{sagun2016singularity}.}{I removed this sentence}

@@

Our work generalizes the local entropy approach above to modern deep networks with continuous weights. It exploits the same phenomenon of wide valleys in the energy landscape but does so without incurring the hardware and communication complexity of replicated training or being limited to models where one can estimate local entropy using belief propagation. The enabling technique in our case is using Markov chain Monte Carlo for estimating the gradient of local entropy, which can be done efficiently even for large deep networks using mini-batch updates.
}

Motivated by the same final goal, viz., flat local minima, the authors in~\citet{hochreiter1997flat} introduce hard constraints on the training loss and the width of local minima and show using the Gibbs formalism~\citep{haussler1997mutual} that this leads to improved generalization. As the authors discuss, the effect of hyper-parameters for the constraints is intricately tied together and they are difficult to choose even for small problems. Our local entropy based objective naturally balances the energetic term (training loss) and the entropic term (width of the valley) and also results in a more scalable algorithm. The ``scope'' $\g$ affords more control on the optimization process than hard constraints and as we discuss in Sec.~\ref{ss:scoping}, this also provides significant computational advantages. The Gibbs formalism used in the analysis of~\citet{hochreiter1997flat} is however a very promising direction to understanding generalization in deep networks in the context of this paper.
%, it bears supercial similarities to the uniform stability analysis~\citep{haussler1997mutual} we employ.
%Recent work by~\citet{keskar2016large} is relevant in the context of the main theme of our paper. The authors estimate the loss in a neighborhood of the weights to argue that small batch size in SGD (i.e., larger gradient noise) generalizes better than large mini-batches and also results in significantly flatter minima.

@@

The gradient of local entropy over a randomly sampled mini-batch of $m$ samples denoted by $\xi_{\ell_i} \in \minibatch{\ell}$ for $i \leq m$ is easy to derive and is given by
\begin{equation}
    -\nabla_x F\rbrac{x, \g;\ \minibatch{\ell}} = \g\ \rbrac{x - \ag{x';\ \minibatch{\ell}}};
    \label{eq:entropysgd_grad}
\end{equation}
where the notation $\ag{\cdot}$ denotes an expectation of its arguments (we have again made the dependence on the data explicit) over a Gibbs distribution of the original optimization problem modified to focus on the neighborhood of $x$; this is given by
\begin{equation}
    \P(x';\ x, \g) \propto\ \exp \sqbrac{-\rbrac{\f{1}{m}\ \sum_{i=1}^m\ f\rbrac{x;\ \xi_{\ell_i}}} - \f{\g}{2}\ \norm{x-x'}_2^2}.
    \label{eq:entropysgd_modified_gibbs}
\end{equation}
Computationally, the gradient in~\eqref{eq:entropysgd_grad} involves estimating $\ag{x';\ \minibatch{\ell}}$ with the current weights fixed to $x$. This is an expectation over a Gibbs distribution and is hard to compute. We can however approximate it using Markov chain Monte-Carlo (MCMC) techniques. In this paper, we use stochastic gradient Langevin dynamics (SGLD)~\citep{welling2011bayesian} that is an MCMC algorithm for drawing samples from a Bayesian posterior and scales to large datasets using mini-batch updates. Please see Sec.~\ref{s:app:langevin} in the Supplement for a brief overview of SGLD. For our application, as lines 3-6 of Alg.~\ref{alg:entropysgd} show, SGLD resembles a few iterations of SGD with additive gradient noise.

@@

\subsubsection{Scoping of $\gamma$}
\label{ss:scoping}

@@

\pc{
\begin{remark}
The above analysis hinges upon an assumption that the Hessian $\nabla^2 f(x)$ does not have eigenvalues in the set $[-2\g-c, c]$ for a constant $c > 0$. This is admittedly unrealistic, for instance, the eigenspectrum of the Hessian at a local minimum in Fig.~\ref{fig:lenet_hessian} has a large fraction of its eigenvalues near zero. Let us however remark that the bound on uniform stability in Thm.~\ref{thm:generalization_bound_nonconvex} by~\citet{hardt2015train} assumes global conditions on the smoothness of the loss function; one imagines that Eqn.~\ref{eq:stability_bound} remains qualitatively the same (with respect to $T$ in particular) even if this assumption is violated to an extent before convergence happens. Obtaining a rigorous generalization bound without this assumption would require a dynamical analysis of SGD and seems out of reach of the current literature.
\end{remark}
}{}

@@

We use stochastic gradient Langevin dynamics (cf. Sec.~\ref{s:app:langevin}) to estimate the gradient of local entropy in Alg.~\ref{alg:entropysgd}. It is natural then, to ask the question whether vanilla SGLD performs as well as local entropy.
%
To this end, we compare the performance of SGLD on two prototypical networks: $\lenet$ on MNIST and $\allcnn$ on CIFAR-10. After a hyper-parameter search, we obtained a test error on $\lenet$ of $0.63 \pm 0.1\%$ after $300$ epochs and $9.89 \pm 0.11\%$ on $\allcnn$ after $500$ epochs. Even if one were to disregard the slow convergence of SGLD, its generalization error is much worse than our experimental results; we get $0.50 \pm 0.01 \%$ on $\lenet$ and $7.81 \pm 0.09 \%$ on $\allcnn$. For comparison, the authors in~\citet{chen2015bridging} report $0.71\%$ error on MNIST on a slightly larger network. Our results with local entropy on RNNs are much better than those reported in~\citet{gan2016scalable} for SGLD. On the PTB dataset, we obtain a test perplexity of $77.656 \pm 0.171$ vs. $94.03$ for the same model whereas we obtain a test perplexity of $1.213 \pm 0.007$ vs. $1.3375$ for $\charlstm$ on the War and Peace dataset.

Training Bayesian deep networks with SGLD, or other more sophisticated algorithms such as SGHMC~\citep{chen2014stochastic,neal2011mcmc} is difficult and the lack of such results in the literature corroborates our experimental results. Roughly speaking, local entropy is so effective because it operates on a transformation of the energy landscape that exploits local entropic effects. Conventional MCMC techniques such as SGLD or Nose'-Hoover thermostats~\citep{ding2014bayesian} can only trade energy for entropy via the temperature parameter which does not allow direct use of the geometric information of the energy landscape and does not help with narrow minima.

>>>>

\todo{Recent works on shallow networks with discrete weights~\citep{baldassi2015subdominant,baldassi2016unreasonable} have shown that the geometrical structure of the energy landscape is characterized by the existence of an exponentially large number of local minima, a large number of narrow isolated minima, and few very dense regions of minima. These dense states have been discovered analytically by adopting an appropriate local entropy measure, and have been shown to be both algorithmically accessible and to have good generalization properties in both random and real-world settings. The original analysis was done in the case of binary weights, and was later generalized by~\citet{baldassi2016multilevel} to the case of weights with an arbitrary number of precision bits. Here, we generalize this approach to the case of deep architectures and continuous weights, and develop a Langevin stochastic gradient descent algorithm based on the local entropy measure.}

This paper presents a new optimization tool for deep learning designed to exploit the local geometric properties of the objective function. \todo{The existence of wide minima in deep networks is also suggested by the spectral analysis of the Hessian~\citep{sagun2016singularity}.} Consider the histogram in Fig.~\ref{fig:lenet_hessian} showing the spectrum of the Hessian at an extremum discovered by Adam~\citep{kingma2014adam} for a convolutional neural network on MNIST~\citep{lecun1998gradient} with about $47,000$ weights (cf.\@ Sec.~\ref{ss:expt:universality}). It is evident that:
\begin{enumerate}[(i)]
\item a large number of directions ($\approx 94\%$) have near-zero eigenvalues (magnitude less than $10^{-4}$),
\item positive eigenvalues (right inset) have a long tail with the largest one being almost $40$,
\item negative eigenvalues (left inset), which are directions of descent that the optimizer missed, have a much faster decay (the largest negative eigenvalue is only $-0.4$).
\end{enumerate}
Interestingly, this trend is not unique to this particular network. Rather, its qualitative properties are shared across a variety of network architectures, sizes, datasets or optimization algorithms (refer to Sec.~\ref{s:expt} for more experiments). Local minima that generalize well and are discovered by gradient descent lie in ``wide valleys'' of the energy landscape, rather than in sharp isolated minima. For an intuitive understanding of this phenomenon, imagine a Bayesian prior concentrated at the minimizer of the expected loss, the marginal likelihood of wide valleys under this prior is much higher than narrow, sharp valleys even if the latter are close to the global minimum in training loss. Almost-flat regions of the energy landscape are robust to data perturbations, noise in the activations, as well as perturbations of the parameters, all of which are widely-used techniques to achieve good generalization. This suggests that wide valleys should result in better generalization and, indeed, standard optimization algorithms in deep learning seem to discover exactly that --- without being explicitly tailored to do so. \todo{For a more detailed recent
analysis of the Hessian, see the parallel work of~\citet{sagun2016singularity}.}

@@

Our work generalizes the local entropy approach above to modern deep networks with continuous weights. It exploits the same phenomenon of wide valleys in the energy landscape but does so without incurring the hardware and communication complexity of replicated training or being limited to models where one can estimate local entropy using belief propagation. The enabling technique in our case is using Langevin dynamics for estimating the gradient of local entropy, which can be done efficiently even for large deep networks using mini-batch updates.
}

Motivated by the same final goal, viz., flat local minima, the authors in~\citet{hochreiter1997flat} introduce hard constraints on the training loss and the width of local minima and show using the Gibbs formalism~\citep{haussler1997mutual} that this leads to improved generalization. As the authors discuss, the effect of hyper-parameters for the constraints is intricately tied together and they are difficult to choose even for small problems. Our local entropy based objective naturally balances the energetic term (training loss) and the entropic term (width of the valley) and also results in a more scalable algorithm. The ``scope'' $\g$ affords more control on the optimization process than hard constraints and as we discuss in Sec.~\ref{s:scoping}, this also provides significant computational advantages. The Gibbs formalism used in the analysis of~\citet{hochreiter1997flat} is however a very promising direction to understanding generalization in deep networks in the context of this paper.
%, it bears supercial similarities to the uniform stability analysis~\citep{haussler1997mutual} we employ.
%Recent work by~\citet{keskar2016large} is relevant in the context of the main theme of our paper. The authors estimate the loss in a neighborhood of the weights to argue that small batch size in SGD (i.e., larger gradient noise) generalizes better than large mini-batches and also results in significantly flatter minima.

@@

The gradient of local entropy over a randomly sampled mini-batch of $m$ samples denoted by $\xi_{\ell_i} \in \minibatch{\ell}$ for $i \leq m$ is easy to derive and is given by
\begin{equation}
    -\nabla_x F\rbrac{x, \g;\ \minibatch{\ell}} = \g\ \rbrac{x - \ag{x';\ \minibatch{\ell}}};
    \label{eq:entropysgd_grad}
\end{equation}
where the notation $\ag{\cdot}$ denotes an expectation of its arguments (we have again made the dependence on the data explicit) over a Gibbs distribution of the original optimization problem modified to focus on the neighborhood of $x$; this is given by
\begin{equation}
    \P(x';\ x, \g) \propto\ \exp \sqbrac{-\rbrac{\f{1}{m}\ \sum_{i=1}^m\ f\rbrac{x';\ \xi_{\ell_i}}} - \f{\g}{2}\ \norm{x-x'}_2^2}.
    \label{eq:entropysgd_modified_gibbs}
\end{equation}
Computationally, the gradient in~\eqref{eq:entropysgd_grad} involves estimating $\ag{x';\ \minibatch{\ell}}$ with the current weights fixed to $x$. This is an expectation over a Gibbs distribution and is hard to compute. We can however approximate it using Markov chain Monte-Carlo (MCMC) techniques. In this paper, we use stochastic gradient Langevin dynamics (SGLD)~\citep{welling2011bayesian} that is an MCMC algorithm for drawing samples from a Bayesian posterior and scales to large datasets using mini-batch updates. Please see Sec.~\ref{s:app:langevin} in the Supplement for a brief overview of SGLD. For our application, as lines 3-6 of Alg.~\ref{alg:entropysgd} show, SGLD resembles a few iterations of SGD with additive gradient noise.

@@

\subsection{Scoping of $\gamma$}
\label{s:scoping}

@@

\pc{
\begin{remark}
The above analysis hinges upon an assumption that the Hessian $\nabla^2 f(x)$ does not have eigenvalues in the set $[-2\g-c, c]$ for a constant $c > 0$. This is admittedly unrealistic, for instance, the eigenspectrum of the Hessian at a local minimum in Fig.~\ref{fig:lenet_hessian} has a large fraction of its eigenvalues almost zero. Let us however remark that the bound on uniform stability in Thm.~\ref{thm:generalization_bound_nonconvex} by~\citet{hardt2015train} assumes global conditions on the smoothness of the loss function; one imagines that Eqn.~\ref{eq:stability_bound} remains qualitatively the same (with respect to $T$ in particular) even if this assumption is violated to an extent before convergence happens. Obtaining a rigorous generalization bound without this assumption would require a dynamical analysis of SGD and seems out of reach of the current literature.
\end{remark}
}{}

@@

We use stochastic gradient Langevin dynamics (cf. Sec.~\ref{s:app:langevin}) to estimate the gradient of local entropy in Alg.~\ref{alg:entropysgd}. It is natural then, to ask the question whether vanilla SGLD performs as well as local entropy.
%
To this end, we compare the performance of SGLD on two prototypical networks: $\lenet$ on MNIST and $\allcnn$ on CIFAR-10. We follow the experiments in~\citep{welling2011bayesian} and~\citep{chen2015bridging} and set the learning rate schedule to be $\eta/(1 + t)^b$ where the initial learning rate $\eta$ and $b$ are hyper-parameters. We make sure that other architectural aspects (dropout, batch-normalization) and regularization (weight decay) are consistent with the experiments in Sec.~\ref{s:expt}.

After a hyper-parameter search, we obtained a test error on $\lenet$ of $0.63 \pm 0.1\%$ after $300$ epochs and $9.89 \pm 0.11\%$ on $\allcnn$ after $500$ epochs. Even if one were to disregard the slow convergence of SGLD, its generalization error is much worse than our experimental results; we get $0.50 \pm 0.01 \%$ on $\lenet$ and $7.81 \pm 0.09 \%$ on $\allcnn$. For comparison, the authors in~\citet{chen2015bridging} report $0.71\%$ error on MNIST on a slightly larger network. Our results with local entropy on RNNs are much better than those reported in~\citet{gan2016scalable} for SGLD. On the PTB dataset, we obtain a test perplexity of $77.656 \pm 0.171$ vs. $94.03$ for the same model whereas we obtain a test perplexity of $1.213 \pm 0.007$ vs. $1.3375$ for $\charlstm$ on the War and Peace dataset.

Training Bayesian deep networks with SGLD, or other more sophisticated algorithms such as SGHMC~\citep{chen2014stochastic,neal2011mcmc} is difficult and the lack of such results in the literature corroborates our experimental results. Roughly speaking, local entropy is so effective because it operates on a transformation of the energy landscape that exploits local entropic effects. Conventional MCMC techniques such as SGLD or Nose'-Hoover thermostats~\citep{ding2014bayesian} can only trade energy for entropy via the temperature parameter which does not allow the direct use of the geometric information of the energy landscape and does not help with narrow minima.
